\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-04-04 reviews/response.Rmd

> p13, l39: "Figure 13 shows the same plot as Figure 12 labelled": You can't jump forward to a figure before all intermediate figures have been introduced. The previous fig was Fig.8. Figs 9-11 have not been mentioned yet. Either rearrange your figures so that 12-13 become 9-10, or use Chinese characters for one of the previously introduced figs (1-8).

Sure. "Figure 13 shows the same plot as Figure 12 labelled" is deleted.

> p13, possible subsection 2.2.6: You seem to have a "sunday = FALSE" default. If TRUE, does this make Sunday the start of the week (as used in the US & Canada)? If so, mention this as an option. No need for a figure.

Done. We deprecate argument `sunday` in favor of `week_start` that appears more general. We added a new subsection on "Start of the week" to briefly explain the option. We have reorganized the order of the subsections to be consistent with the function argument's ordering.

@@

> p13, possible subsection 2.2.7: How can you enter specific holidays? These are different from country to country, e.g., based on national holidays such as Thanksgiving, Labor Day, independence days, religious holidays, etc.

We used `tsibble::holiday_aus()` for generating Australian public holidays, prior to creating calendar displays. Whether to use holidays or not is a data-specific problem, which is beyond the scope of the calendar plot.

### 2019-04-04 main.Rmd
new subsection on "Start of the week"

```
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, scale = "fixed", 
  width = 0.95, height = 0.95, margin = NULL)
```

@@

>>>>

```
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
  week_start = 1, nrow = NULL, ncol = NULL, polar = FALSE, scale = "fixed", 
  width = 0.95, height = 0.95, margin = NULL)
```

@@

The start of the week for a monthly calendar is adjustable. The default is Monday (`1`), which is chosen from the data perspective. The week, however, can begin with Sunday (`7`) as commonly used in the US and Canada, or other week day subject to different countries and cultures.

### 2019-04-04 main.tex
new subsection on "Start of the week"

\begin{verbatim}
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, scale = "fixed", 
  width = 0.95, height = 0.95, margin = NULL)
\end{verbatim}

@@

>>>>

\begin{verbatim}
frame_calendar(data, x, y, date, calendar = "monthly", dir = "h", 
  week_start = 1, nrow = NULL, ncol = NULL, polar = FALSE, scale = "fixed", 
  width = 0.95, height = 0.95, margin = NULL)
\end{verbatim}

@@

The start of the week for a monthly calendar is adjustable. The default is Monday (\texttt{1}), which is chosen from the data perspective. The week, however, can begin with Sunday (\texttt{7}) as commonly used in the US and Canada, or other week day subject to different countries and cultures.
